### 2010-03-19 doc/manuals/configuration/configuration_manual.tex
Switching documents to bibliography style which is supposed to be present in latex distributions. Fixes in some documents and build procedures.
Minor corrections.

\documentclass{article}
%\documentclass{book}
\usepackage{graphicx}                              %for PNG images (pdflatex)
\usepackage[linkbordercolor={1.0 1.0 0.0}]{hyperref} %for \url tag
\usepackage{color}                                 %for defining custom colors
\usepackage{framed}                                %for shaded and framed paragraphs
\usepackage{textcomp}                              %for various symbols, e.g. Registered Mark
\usepackage{geometry}                              %for defining page size
\usepackage{longtable}                             %for breaking tables
\usepackage{array}
\usepackage{booktabs}
%
\geometry{verbose,a4paper,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=2cm}
\hypersetup{
  pdfauthor = {Martin Skou Andersen},
  pdftitle = {WS-ARC service configuration manual},
  pdfsubject = {Paper subject},
  pdfkeywords = {Paper,keyword,comma-separated},
  pdfcreator = {PDFLaTeX with hyperref package},
  pdfproducer = {PDFLaTeX}
}
%
\bibliographystyle{IEEEtran}                       %a nice bibliography style
%
\def\efill{\hfill\nopagebreak}%
\hyphenation{Nordu-Grid}
\setlength{\parindent}{0cm}
\setlength{\FrameRule}{1pt}
\setlength{\FrameSep}{8pt}
\addtolength{\parskip}{5pt}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\renewcommand{\arraystretch}{1.3}
\newcommand{\dothis}{\colorbox{shadecolor}}
\newcommand{\ngdl}{\url{http://ftp.nordugrid.org/download}~}
\definecolor{shadecolor}{rgb}{1,1,0.6}
\definecolor{salmon}{rgb}{1,0.9,1}
\definecolor{bordeaux}{rgb}{0.75,0.,0.}
\definecolor{cyan}{rgb}{0,1,1}
\definecolor{grey}{rgb}{0.9,0.9,0.9}

@@

\subsubsection{TLS MCC}\label{sec:tls-mcc}
A security layer can be configured with the TLS MCC, named \texttt{tls.service},
and it should be put on top of a TCP MCC. By default it is able to understand
the SSLv2 (hadshake only), SSLv3 and TLSv1 protocols, however the \texttt{Handshake}
element can be used to specify another behaviour. The supported values for the
\texttt{Handshake} element are \texttt{TLS} (default) and \texttt{SSLv3}, where
specifying the latter will configure a MCC which only understand the SSLv3
protocol. If other values than the mentioned ones are given, then \texttt{TLS}
will be used.

@@

\section{The \texttt{arched} daemon}\label{sec:arched}
The \texttt{arched} daemon is the daemon which is used to start every service in
WS-ARC. It will load a configuration file, and start the services specified
herein.

>>>>

\documentclass{article}
%\documentclass{book}
\usepackage{graphicx}                              %for PNG images (pdflatex)
\usepackage[linkbordercolor={1.0 1.0 0.0}]{hyperref} %for \url tag
\usepackage{color}                                 %for defining custom colors
\usepackage{framed}                                %for shaded and framed paragraphs
\usepackage{textcomp}                              %for various symbols, e.g. Registered Mark
\usepackage{geometry}                              %for defining page size
\usepackage{longtable}                             %for breaking tables
\usepackage{array}
\usepackage{booktabs}
%
\geometry{verbose,a4paper,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=2cm}
\hypersetup{
  pdfauthor = {Martin Skou Andersen},
  pdftitle = {WS-ARC service configuration manual},
  pdfsubject = {Paper subject},
  pdfkeywords = {Paper,keyword,comma-separated},
  pdfcreator = {PDFLaTeX with hyperref package},
  pdfproducer = {PDFLaTeX}
}
%
\usepackage[numbers]{natbib}
\bibliographystyle{plainnat}
%
\def\efill{\hfill\nopagebreak}%
\hyphenation{Nordu-Grid}
\setlength{\parindent}{0cm}
\setlength{\FrameRule}{1pt}
\setlength{\FrameSep}{8pt}
\addtolength{\parskip}{5pt}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\renewcommand{\arraystretch}{1.3}
\newcommand{\dothis}{\colorbox{shadecolor}}
\newcommand{\ngdl}{\url{http://ftp.nordugrid.org/download}~}
\definecolor{shadecolor}{rgb}{1,1,0.6}
\definecolor{salmon}{rgb}{1,0.9,1}
\definecolor{bordeaux}{rgb}{0.75,0.,0.}
\definecolor{cyan}{rgb}{0,1,1}
\definecolor{grey}{rgb}{0.9,0.9,0.9}

@@

\subsubsection{TLS MCC}\label{sec:tls-mcc}
A security layer can be configured with the TLS MCC, named \texttt{tls.service},
which is based on the OpenSSL library~\cite{openssl}, and it should be put on
top of a TCP MCC. By default it is able to understand
the SSLv2 (hadshake only), SSLv3 and TLSv1 protocols, however the \texttt{Handshake}
element can be used to specify another behaviour. The supported values for the
\texttt{Handshake} element are \texttt{TLS} (default) and \texttt{SSLv3}, where
specifying the latter will configure a MCC which only understand the SSLv3
protocol. If other values than the mentioned ones are given, then \texttt{TLS}
will be used.

@@

\section{The \texttt{arched} daemon}\label{sec:arched}
The \texttt{arched} daemon is the daemon which is used to host every service in
WS-ARC. It will load a configuration file, and host the services specified
herein.
